---
title: "bibliometric_analysis"
output: html_document
---


# Web of Science

Re-running the same search parameters returned 1397 results (a few more than originally provided).

Link to query: https://www.webofscience.com/wos/woscc/summary/09ad7c24-14b3-435b-9eab-a6e53518a168-0022b2f2/date-ascending/1

```{r WoS, echo=FALSE, results="show", message=FALSE}
library(bibliometrix)

wos_data <- convert2df(file = "data/webofscience_1-1397.txt", dbsource = 'wos',
                       format = 'plaintext')
wos_results <- biblioAnalysis(wos_data, sep = ";")

wos_summary <- summary(wos_results)

plot(wos_results)
print(wos_summary)


# CR <- citations(wos_data, field = "article", sep = ";")
# cbind(CR$Cited[1:10])

CR_local <- localCitations(wos_data, sep = ";")
CR_local$Authors[1:10,]
CR_local$Papers[1:10,]


```




# Scopus

Re-running search parameters for Scopus returned 1770 results.

link to query: TITLE-ABS-KEY ( "climate justice"  OR  "environmental justice"  OR  "social justice"  AND  "climate change"  OR  "Global warming" )  AND  ( LIMIT-TO ( DOCTYPE ,  "ar" )  OR  LIMIT-TO ( DOCTYPE ,  "ch" )  OR  LIMIT-TO ( DOCTYPE ,  "re" )  OR  LIMIT-TO ( DOCTYPE ,  "bk" )  OR  LIMIT-TO ( DOCTYPE ,  "ed" ) )  AND  ( LIMIT-TO ( LANGUAGE ,  "English" ) )  AND  ( LIMIT-TO ( SRCTYPE ,  "j" )  OR  LIMIT-TO ( SRCTYPE ,  "b" )  OR  LIMIT-TO ( SRCTYPE ,  "k" ) ) 

```{r scopus, echo=FALSE, results="show", message=FALSE}
# library(bibliometrix)
scopus_data <- convert2df(file = "data/scopus_1770.bib", dbsource = 'scopus',
                       format = 'bibtex')
scopus_results <- biblioAnalysis(scopus_data, sep = ";")

scopus_summary <- summary(scopus_results)

plot(scopus_results)
print(scopus_summary)


```
